A generic and fast C++ optimization framework

### 2017-10-21 paper.tex
Add references for each library in Table 1.

However, the current landscape of optimization frameworks for machine learning
is not particularly comprehensive.  A variety of tools such as
Caffe \cite{jia2014caffe},
% mxnet ??
TensorFlow \cite{abadi2016tensorflow},
and
Keras \cite{chollet2015}
have optimization frameworks, but they are limited to SGD-type optimizers and
are only able to optimize deep neural networks or related structures.  Thus
expressing arbitrary machine learning objective functions can be difficult or in
some cases not possible.  Other libraries, like
% Shogun \cite{shogun}
%and
scikit-learn \cite{pedregosa2011scikit},
do have optimizers, but generally not in a coherent framework and
often the implementations may be specific to an individual machine learning
algorithm.  At a higher level, many programming languages may have generic
optimizers, like SciPy \cite{jones2014scipy} and MATLAB, but typically these
optimizers are not suitable for large-scale machine learning tasks where, e.g.,
calculating the full gradient of all of the data may not be feasible.  Table
\ref{tab:features} provides a rough overview.

@@

        & mlpack             & \CIRCLE & \CIRCLE & \CIRCLE & \CIRCLE & \CIRCLE & \CIRCLE & \CIRCLE \\

@@

        & shogun             & \CIRCLE & - & \CIRCLE & \CIRCLE & \CIRCLE & - & -

@@

        & vowpal wabbit      & - & - & \CIRCLE  & - & - & - &

@@

        & TensorFlow         & \CIRCLE & -  & \CIRCLE  & \LEFTcircle & - &

@@

        & caffe             & \CIRCLE & -  & \CIRCLE & \LEFTcircle & \LEFTcircle

@@

        & keras             & \CIRCLE & -  & \CIRCLE & \LEFTcircle & \LEFTcircle

@@

        & scikit-learn       & \LEFTcircle & - & \LEFTcircle  & \LEFTcircle & -

@@

        & scipy              & \CIRCLE & \CIRCLE  & -  & \CIRCLE & - & - & - \\

@@

        & MATLAB             & \CIRCLE & \CIRCLE & - & \CIRCLE & - & - & - \\

>>>>

However, the current landscape of optimization frameworks for machine learning
is not particularly comprehensive.  A variety of tools such as
Caffe \cite{jia2014caffe},
% mxnet ??
TensorFlow \cite{abadi2016tensorflow},
and
Keras \cite{chollet2015}
have optimization frameworks, but they are limited to SGD-type optimizers and
are only able to optimize deep neural networks or related structures.  Thus
expressing arbitrary machine learning objective functions can be difficult or in
some cases not possible.  Other libraries, like
% Shogun \cite{shogun}
%and
scikit-learn \cite{pedregosa2011scikit},
do have optimizers, but generally not in a coherent framework and
often the implementations may be specific to an individual machine learning
algorithm.  At a higher level, many programming languages may have generic
optimizers, like SciPy \cite{jones2014scipy} and MATLAB \cite{mathworks2017OTB}, but typically these
optimizers are not suitable for large-scale machine learning tasks where, e.g.,
calculating the full gradient of all of the data may not be feasible.  Table
\ref{tab:features} provides a rough overview.

@@

        & mlpack \cite{mlpack2013}            & \CIRCLE & \CIRCLE & \CIRCLE & \CIRCLE & \CIRCLE & \CIRCLE & \CIRCLE \\

@@

        & shogun \cite{sonnenburg2010shogun}             & \CIRCLE & - & \CIRCLE & \CIRCLE & \CIRCLE & - & -

@@

        & vowpal wabbit \cite{Langford2007VW}      & - & - & \CIRCLE  & - & - & - &

@@

        & TensorFlow \cite{abadi2016tensorflow}        & \CIRCLE & -  & \CIRCLE  & \LEFTcircle & - &

@@

        & caffe \cite{jia2014caffe}           & \CIRCLE & -  & \CIRCLE & \LEFTcircle & \LEFTcircle

@@

        & keras \cite{chollet2015}            & \CIRCLE & -  & \CIRCLE & \LEFTcircle & \LEFTcircle

@@

        & scikit-learn \cite{pedregosa2011scikit}       & \LEFTcircle & - & \LEFTcircle  & \LEFTcircle & -

@@

        & scipy \cite{jones2014scipy}             & \CIRCLE & \CIRCLE  & -  & \CIRCLE & - & - & - \\

@@

        & MATLAB \cite{mathworks2017OTB}            & \CIRCLE & \CIRCLE & - & \CIRCLE & - & - & - \\
